# Statistical testing using R
## Table of contents

## Data
Load the data set into the R environment. This data set has been collected by Walmart for researching variables that might influence the CPI score (**C**onsumer **p**rice **i**ndex).
[DOWNLOAD HERE]()


```{r}
### your code here ###
```


## Simple plots
Making some simple plots is a smart way of knowing our data set in the first stage. Try to make all following plots. What conclusion can you make by observing?

#### A side-by-side boxplot
```{r}
### your code here ###
```


#### A scatter plot. x: Unemployment, y: CPI
```{r}
### your code here ###
```



## Descriptive statistics
Calculate **sample size**, **Mean**, **SD**, **variance** and **IQR** of CPI each year and present it in a table. This should be a data frame or a matrix with six columns.

```{r}
### your code here ###
```


## t-test
#### Test if the CPI score in 2010 and 2012 are the same.
Assume that the population variances are not the same. 
- _Which t-test should you choose?_  
- _What’s your hypothesis? (H0 vs H1)_  

Run the test in R. What are your conclusions?

```{r}
### your code here ###
```

#### Test if the fuel price in 2010 and 2012 are the same.
Then, assume that the population variance is the same.
- _Which t-test should you choose?_
- _What’s your hypothesis?_  

Run the test in R. 

- _What’s your conclusion?_  

```{r}
### your code here ###
```

## Correlation coefficient
Calculate the pairwise correlation between year, temperature, and fuel price. Present it in both the plot (scatter plot) and correlation matrix.

```{r}
### your code here ###
```


```{r}
### your code here ###
```


## Advanced
Try this section after you finish all previous sections.

### Fancy plots
#### make a scatter plot coloured by year.

```{r}
### your code here ##

```

#### create a density plot, correlation coefficient score, and confidence interval.
 _(HINT: ```??pairs.panels```)_

```{r}
# install.packages('psych')
library(psych)
### your code here ###

```


### The simple linear regression model

#### Fit a simple linear regression model:
Independent variable: CPI (x) - Dependent variable: Fuel price (y)

 - _What does the p-value in the returned table stand for?_ - What is the formula of this model?


```{r}
### your code here ###
```


#### Draw the scatter plot and the fitted regression line.

```{r}
### your code here ###
```

### Draw the residuals plot.
- _How well is the variance of CPI  explained by the fuel price?_

```{r}
### your code here ###
```



### Discrete data
For this section we will try to fit a linear model with independent variables that are of a discrete data type.

Fit a model for CPI with store, year, temperature, fuel price, and unemployment rate as explanatory variables. Note that store and year should be considered categorical data in this case.

This will return a long table. When we consider categorical information as a dependent variable, We use a dummy variable for the calculations.

- _What are the reference points for stores and years?_
```{r}
### your code here ###
```

### Draw the residual plot again
- _Can CPI be explained better, using this model?_

```{r}
### your code here ###
```


### ANOVA
Fit a two-way ANOVA model: CPI = Store + year + e. 
- _Do your degrees of freedom make sense? (If it is 1, you may forget to convert your data type as factor)_ 
- _What conclusion can you draw from these results?_

```{r}
### your code here ###
```
